### 2014-04-15 docs/seminar/casestudy.tex
changed abstract and others
changed the intro and the case study section, as well as part of the methods

\section{Case Study}
\label{sec:casestudy}
Essential components of the platform as well as the work-flow of searching for the translators are depicted in Figure \ref{fig:architecture}. The platform consist of four main components: \textit{Ranking}, \textit{Proficiency Estimator}, \textit{Scheduler} and \textit{Profiles}.

\begin{figure*}[h]
\begin{center}
\includegraphics[scale=0.8]{figures/dataflow.png}
\caption{Translator-Expert Search Work Flow
\label{fig:architecture}}
\end{center}
\end{figure*}

The \textit{Profiles} stores translator profile information i.e. source and target languages, offered price and translation duration per word. The \textit{Scheduler} system figures out the delivery time based on timetable of translators. The scheduler builds an efficient data structure to calculate the delivery time in a reasonable response time. The details of the process are out of scope of the paper. The \textit{Proficiency Estimator} system stores the previous-translated documents and indexes them using Lucene. The similarity between query and indexed documents is used as a basis for the estimation of translator's proficiency. In fact, the proficiency value is achieved by aggregating the documents similarity scores. The applied aggregation function is described in Section\ref{sec:apply}. At last, the \textit{Ranking} system uses all the data provided in the previous steps to create the ranking model. The \textit{Ranking} system applies Learning to Rank techniques to return the most related translators to the client. The training data is provided by a group of annotators who are familiar with the business of company using an evaluation system. The evaluation system suggests three translators and the annotators rate them by comparing between their factors. In order to prevent bias in evaluation, the translators are suggested randomly and without name and picture. Applied learning to rank methods and results are described in Section\ref{sec:apply}.

@@

Beside the mentioned work-flow after finishing the translation, another expert called proofreader revises the translation. The proofreader is selected by the client and guarantees the quality of the final translation. As well as revising, the proofreader assesses the quality of translator's task from different points of view (grammar, style, accuracy, content and language). The assessment value can be from $1$ (very bad) to $5$ (perfect). As it is described in Section\ref{sec:apply}, we use these assessments to evaluate and compare aggregation algorithms.

>>>>

\section{Translator recommendation}
\label{sec:casestudy}
\subsection{Use-case}\label{sec:usecase}
The user model for this application is that of an online user in possession of a document in a language other than the desired one. The need for a different language comes either from an internal need to know the contents of the document, or from an external requirement to provide the document in a high-quality translation in the desired language. However, the document is not simply an official document (e.g. a birth certificate) since the platform does not provide legal translation services. Therefore, we can assume that the document to be translated has a particular narrative and a certain topic.

The task of this user is to identify a translator who balances translation quality with non-functional requirements such as cost and delivery time.

The system is therefore charged to estimate the proficiency of the translator on the topic of the document at hand by considering previously translated documents, and to learn a preference model that a typical user will have in combining this proficiency estimation with the other aspects involved in the decision making process (monetary, temporal and social). A reasonable hypothesis, which we will verify in what follows, is that a high-proficiency, low-cost, fast-delivery, professionally known translator will be preferred.

\subsection{The Platform}\label{sec:platform}
Essential components of the platform as well as the work-flow of searching for the translators are depicted in Figure \ref{fig:architecture}. The platform consist of four main components: \textit{Ranking}, \textit{Proficiency Estimator}, \textit{Scheduler} and \textit{Profiles}.

\begin{figure*}
\begin{center}
\includegraphics[width=12cm]{figures/dataflow.png}
\caption{Translator-Expert Search Work Flow
\label{fig:architecture}}
\end{center}
\end{figure*}

The \textit{Profiles} stores translator profile information i.e. source and target languages, offered price and translation duration per word, and the number of translations the translator has performed for the same client. The \textit{Scheduler} system figures out the delivery time based on timetable of translators. The scheduler builds an efficient data structure to calculate the delivery time in a reasonable response time. The details of the process are out of scope of the paper. The \textit{Proficiency Estimator} system stores the previously-translated documents and indexes them using Lucene. The similarity between query and indexed documents is used as a basis for the estimation of translator's proficiency. In fact, the proficiency value is achieved by aggregating the documents similarity scores. The applied aggregation function is described in Section\ref{sec:apply}. At last, the \textit{Ranking} system uses all the data provided in the previous steps to create the ranking model. The \textit{Ranking} system applies Learning to Rank techniques to return the most related translators to the client. The training data is provided by a group of annotators who are familiar with the business of company using an evaluation system. The evaluation system suggests three translators and the annotators rate them by comparing between their factors. In order to prevent bias in evaluation, the translators are suggested randomly and without name and picture. Applied learning to rank methods and results are described in Section\ref{sec:apply}.

@@

Separately from the mentioned workflow, after finishing the translation, another expert (a  proofreader) revises the translation. The proofreader is selected by the client and guarantees the quality of the final translation. As well as revising, the proofreader assesses the quality of translator's task from different points of view (grammar, style, accuracy, content and language). The assessment value can be from $1$ (very bad) to $5$ (perfect). In Section\ref{sec:apply} we use these assessments to evaluate and compare aggregation algorithms.

### 2014-04-15 docs/seminar/introduction.tex
changed the intro and the case study section, as well as part of the methods

\section{Introduction}
\label{sec:introduction}
The goal of expertise retrieval is to link humans to expertise areas, and vice versa. In other words, the task of expertise retrieval is to identify a set of persons with relevant expertise for the given query \citep{er, er-community-aware}.

With the development of information retrieval (IR) techniques, many research efforts in this field have been made to address high-level IR such as entity retrieval and expertise retrieval \citep{er-sparse}  and not just traditional document retrieval. The launch of the Expert Finding task at TREC has generated a lot of interest in expertise retrieval, with rapid progress being made in terms of modeling, algorithms, and evaluation aspects \citep{trec2005, er-community-aware}.

Two principal approaches are proposed by \citet{trec2005} based on probabilistic language modeling techniques. They were formalized as so-called candidate models and document models. The candidate-based approach, also referred to as profile-based method, builds a textual representation of candidate experts and then ranks them based on the query. The document models first find documents relevant to the topic and then locate the experts associated with these documents \citep{er}.

Ranking techniques are an essential part of each IR framework. In recent years, Learning to Rank (L2R) has been studied extensively especially for document retrieval. It refers to machine learning techniques for training the model in a ranking task \citep{er}. In essence, expert search is a ranking problem and thus the existing L2R techniques can be naturally applied to it \citep{l2r-intro}.

As well as ranking techniques, aggregation functions have a significant effect on the performance of expert retrieval systems. Aggregate tasks are those where documents' similarities are not
the final outcome, but instead an intermediary component. In expert search, a ranking of candidate persons with relevant expertise to a query is generated after aggregation of their related documents \citep{agg-learning}.

This paper addresses the problem of searching translators as experts. We offer a novel translator-expert retrieval platform and evaluate different expert retrieval methods based on the practical implementation of the platform. In contrast to common expert retrieval systems, we include significant factors of searching a translator (like price and delivery time) in the study as well as the relevance of the documents to the query document. We have applied Learning to Rank in a candidate-based approach. Additionally, different aggregation algorithms related to documents of translators have been studied.

The remaining of the paper is organized as follows. In Section \ref{sec:casestudy}, the Translator-Expert Retrieval framework is described in detail. Then, Section \ref{sec:methods} explains methods used in the study. In Section \ref{sec:apply}, we report the result of applied methods on the framework. Finally, we conclude the study in Section \ref{sec:conclusion}.

>>>>

\section{Introduction}
\label{sec:introduction}
We look at the technology of Information Retrieval from the perspective of a real-world user scenario involving the selection of human translators based on a combination of expertise and practical factors. 
It has become more and more common place to consider search technology in a series of applications previously served only by database technology, if at all by a computer system~\cite{Grefenstette:2011}. In such cases, new data, new users, and new scenarios need to be observed, existing methods have to be adapted to the task at hand, and new evaluation procedures have to be devised.

This paper addresses the problem of searching translators as experts. We offer a novel translator-expert retrieval platform and evaluate different expert retrieval methods based on the practical implementation of the platform. In contrast to common expert retrieval systems, we include significant factors of searching a translator (such as price and delivery time) in the automated decision process as well as the relevance of the documents each translator has previously translated to the query document. The proposed method has two distinct components: A proficiency estimation phase, in which different aggregation algorithms related to documents of translators have been studied and compared; and a Learning-to-Rank phase in which different features are tested under all state of the art Learning-to-Rank methods based on a manually created ground truth, which we make available together with the source code of our application under GPL\footnote{\url{http://github/anonymized}}.

The remaining of the paper is organized as follows. In Section\ref{sec:casestudy}, the use-case is presented and the Translator-Expert Retrieval framework is described in detail. Then, Section\ref{sec:methods} explains the methods used in the study. Section\ref{sec:apply} shows the result of applied methods on the framework. We discuss these results and conclude the study in Section\ref{sec:conclusion}.

### 2014-04-15 docs/seminar/methods.tex
changed the intro and the case study section, as well as part of the methods

\section{Methods and Related Work}
\label{sec:methods}
In this section, we study different methods and algorithms regarding to Aggregation Functions and Learning to Rank.

\subsection{Aggregation Functions}
The aggregation function has a significant impact on the performance of Expert Retrieval system. As a usual scenario in expert retrieval systems, first each document related to an expert is scored and ranked regarding to query. Then, the top $N$ document scores associated with a candidate expert are aggregated in order to rank the experts.

>>>>

\section{Methods and Related Work}
\label{sec:methods}
With the development of information retrieval (IR) techniques, many research efforts go beyond traditional document retrieval and address high-level IR such as entity retrieval and expertise retrieval \cite{er-sparse}. The goal of expertise retrieval is to link humans to expertise areas, and vice versa. In other words, the task of expertise retrieval is to identify a set of persons with relevant expertise for the given query \cite{er,er-community-aware}.
The launch of the Expert Finding task at TREC has generated a lot of interest in expertise retrieval, following by rapid progress being made in terms of modeling, algorithms, and evaluation aspects \cite{trec2005,er-community-aware}.

\cite{trec2005} propose two principal approaches  in the expertise retrieval area based on probabilistic language modeling techniques. They were formalized as so-called \textit{candidate models} and \textit{document models}. The candidate-based approach, also referred to as profile-based method, builds a textual representation of candidate experts and then ranks them based on the query. The document models first find documents relevant to the topic and then locate the experts associated with these documents \cite{er}.

Ranking techniques are an essential part of each IR framework. In recent years, Learning to Rank (L2R) has been studied extensively especially for document retrieval. It refers to machine learning techniques for training the model in a ranking task \cite{er}. In essence, expert search is a ranking problem and thus the existing L2R techniques can be naturally applied to it \cite{l2r-intro}.

As well as ranking techniques, aggregation functions have a significant effect on the performance of expert retrieval systems. Aggregate tasks are those where documents' similarities are not
the final outcome, but instead an intermediary component. In expert search, a ranking of candidate persons with relevant expertise to a query is generated after aggregation of their related documents \cite{agg-learning}.
\subsection{Aggregation Functions}
The aggregation function has a significant impact on the performance of Expert Retrieval system. As a usual scenario in expert retrieval systems, first each document related to an expert is scored and ranked regarding to query. Then, the top $N$ document scores associated with a candidate expert are aggregated in order to rank the experts.
